---
title: A Tidyverse Primer
author: David Kane and Pratham Kancherla
tutorial:
  id: a-tidyverse-primer
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: 'Tutorial for Chapter 2: A Tidyverse Primer'
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
library(tidymodels)
library(lubridate)
library(readr)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 600, 
        tutorial.storage = "local") 

df <- data.frame("column 1" = 1:3, `two` = 4:6, check.names = FALSE)
tbl <- tibble(`column 1` = 1:3, `two` = 4:6)
url <- "https://data.cityofchicago.org/api/views/5neh-572f/rows.csv?accessType=DOWNLOAD&bom=true&format=true"

chicago <- read_csv(url)

add_numbers <- function(num1, num2){
  sum <- num1 + num2
  return(sum)
}

compute_log_ratio <- function(mpg, wt, log_base = exp(1)) {
  (log(mpg/wt, base = log_base))
}
result <- compute_log_ratio(mtcars$mpg, mtcars$wt)
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

## Introduction
### 

This tutorial covers [Chapter 2: Tidyverse Principles](https://www.tmwr.org/tidyverse.html#tidyverse-principles) from [*Tidy Modeling with R*](https://www.tmwr.org/) by Max Kuhn and Julia Silge. We briefly discuss important principles of the [*Tidyverse*](https://www.tidyverse.org) design philosophy and how they apply in the context of modeling software that is easy to use properly and supports good statistical practices. The [**tidymodels**](https://www.tidymodels.org/) and the [**tidyverse**](https://tidyverse.tidyverse.org/) packages build on the R language, and [**tidymodels**](https://www.tidymodels.org/packages/) applies *Tidyverse* principles to building models.

## Tidyverse principles
### 

The full set of strategies and tactics for writing R code in the *Tidyverse* style can be found at this [website](https://design.tidyverse.org). Here we can briefly describe several of the general *Tidyverse* design principles, their motivation, and how we think about modeling as an application of these principles.

### Exercise 1

Load the **tidyverse** library.

```{r tidyverse-principles-1, exercise = TRUE}

```

```{r tidyverse-principles-1-hint-1, eval = FALSE}
library(...)
```

### 

At first we will not be using the **tidyverse** functions, as we are trying to understand the core language of R.

### Exercise 2

Type `mtcars` and hit "Run Code."

```{r tidyverse-principles-2, exercise = TRUE}

```

```{r tidyverse-principles-2-hint-1, eval = FALSE}
mtcars
```

### 

`mtcars` is an R data frame with information about `r dim(mtcars)[1]` cars.

### Exercise 3

Next, we will extract the information regarding the first row of `mtcars`. In square brackets, next to `mtcars`, put `1,` and hit "Run Code."

```{r tidyverse-principles-3, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-principles-3-hint-1, eval = FALSE}
mtcars[..., ]
```

### 

We can now see that every column of the first row in `mtcars` is printed.

### Exercise 4

Next, we will try extracting the second and fourth row. Copy the previous code from before and inside the brackets, remove `1,` and select the rows `2,4` using `c()`. Remember to use a `,` after you put the vector in the bracket.

```{r tidyverse-principles-4, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-principles-4-hint-1, eval = FALSE}
mtcars[...(2, 4), ]
```

```{r include = FALSE}
mtcars[c(2, 4), ]
```

### 

Now you can see every column printed for the second and fourth row of `mtcars`.

### Exercise 5

Now we will look at the `gear` column in `mtcars`. Extract `gear` from `mtcars` using `$`.

```{r tidyverse-principles-5, exercise = TRUE}

```

```{r tidyverse-principles-5-hint-1, eval = FALSE}
...$gear
```

```{r include = FALSE}
mtcars$gear
```

### 

Each car in `mtcars` has a listed amount of gears ranging from 3 to 5. This can be ordered, however.

### Exercise 6

To understand the functionality of `order()`, pass in a vector argument of `6, 9, 8` using `c()`.

```{r tidyverse-principles-6, exercise = TRUE}

```

```{r tidyverse-principles-6-hint-1, eval = FALSE}
order(...(6, 9, 8))
```

```{r include = FALSE}
order(c(6, 9, 8))
```

### 

The `order()` does not order the elements as entered in the arguments, but rather sorts them and returns the index of each value.

### Exercise 7

Copy the previous code. Now, instead, pass `mtcars$gear` as the argument.

```{r tidyverse-principles-7, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-principles-7-hint-1, eval = FALSE}
order(mtcars$...)
```

```{r include = FALSE}
order(mtcars$gear)
```

### 

The `order()` sorts a string vector by looking at the first letter of each string and sorting it in alphabetical order, returning the indexes of the words in the vector.

### Exercise 8

Copy the previous code. In `mtcars[]`, pass in the previous code in the brackets. Don't forget the `,` after the `order()` expression within the brackets!

```{r tidyverse-principles-8, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-principles-8-hint-1, eval = FALSE}
mtcars[order(...$gear), ]
```

```{r include = FALSE}
mtcars[order(mtcars$gear), ]
```

### 

As you can see, the mtcars data frame column `gear` is ordered from *descending* order using the `order()` function.

### Exercise 9

Copy the previous code. Add `mtcars$mpg` into the `order()` function. Don't forget the `,` after the `order()` expression within the brackets!

```{r tidyverse-principles-9, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-principles-9-hint-1, eval = FALSE}
mtcars[order(mtcars$..., mtcars$...), ]
```

```{r include = FALSE}
mtcars[order(mtcars$gear, mtcars$mpg), ]
```

### 

We have now successfully order the data frame `mtcars` by `mpg` and `gears`. You can see that for each `gear` value, the `mpg` is in descending order.

### Exercise 10

Run the code below.

```{r tidyverse-principles-10, exercise = TRUE}
arrange(.data = mtcars, gear, mpg)

```

### 

Notice that the output is the exactly similar in Exercise 9. This is the way order a data frame using the `tidyverse` function `arrange()`.

Great job! You have learned the core language of R and compared its functionality to the `tidyverse` package.

### 

## Reuse Existing Data Structures
### 

<!-- Fix this intro -->

Whenever possible, functions should avoid returning a novel data structure. This reduces the cognitive load when using software; no additional syntax or methods are required.

### 

We will be using the **rsample** package to give an example of using existing data structures that make statistical calculations happen quicker and more efficient.

### Exercise 1

Load the `rsample` library.

```{r reuse-existing-data--1, exercise = TRUE}

```

```{r reuse-existing-data--1-hint-1, eval = FALSE}
library(...)
```

```{r include = FALSE}
library(rsample)
```

### Exercise 2

Get a better understanding of the **rsample** library by typing in `?rsample` into the console. Look at the description in the help tab. CP/CR.

```{r reuse-existing-data--2}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```

### 

The **rsample** package makes it easier to store data. Resampling allows us to make more accurate predictions and gather more information about a sample.

### 

One resampling method is called bootstrap, which is resampling a single data set to create many simulated samples. This can be done by using the `bootstraps()`.

### Exercise 3

Find out more about `bootstraps` by typing `?bootstraps`in the console. Look at the description. CP/CR

```{r reuse-existing-data--3}
question_text(NULL,
	answer(NULL, correct = TRUE),
	allow_retry = TRUE,
	try_again_button = "Edit Answer",
	incorrect = NULL,
	rows = 3)
```


### Exercise 4

We will explore **rsample** using the bootstrap method. Access `bootstraps()` from the **rsample** library using `::`.

```{r reuse-existing-data--4, exercise = TRUE}

```

```{r reuse-existing-data--4-hint-1, eval = FALSE}
...::bootstraps()
```

<!-- DK: Shouldn't error = TRUE work here? -->

```{r include = FALSE}
#rsample::bootstraps()

```

This will throw an error, because a data frame was not specified. Our data frame is `mtcars`.

### Exercise 5

Using the previous code, enter `mtcars` in `bootstraps()`.

```{r reuse-existing-data--5, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r reuse-existing-data--5-hint-1, eval = FALSE}
rsample::bootstraps(...)
```

```{r include = FALSE}
rsample::bootstraps(mtcars)
```

### 

As you can see, this outputs 25 rows of bootstraps. But we only want 3 bootstrap splits.

### Exercise 6

Using the previous code, only produce 3 splits using the `times` parameter in `bootstraps()`.

```{r reuse-existing-data--6, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r reuse-existing-data--6-hint-1, eval = FALSE}
rsample::bootstraps(mtcars, ... = 3)
```

```{r include = FALSE}
rsample::bootstraps(mtcars, times = 3)
```

### 

One important feature in the tibble produced by **rsample** is that the *splits* column is a list. In this instance, each element of the list has the same type of object: an `rsplit` object that contains the information about which rows of `mtcars` belong in the bootstrap sample.

### 

Great Job! You understood the meaning and importance of resampling using the bootstrap method. This was achieved using the `bootstrap()` method from the **rsample** library.

## Design for the Pipe and Functional Programming
### 

We are used to using the conventional pipe operator `|>` and using simple lines of code to produce a desired output. We will revisit this useful pipe operator and how to reduce complexity when using functions.

### Exercise 1

We will be revisiting the `|>` pipe operator using `mtcars`. We will be looking at how data visualization can be more readable.

First, as seen in the previous section, run the code below.

```{r design-for-the-pipe--1, exercise = TRUE}
arrange(mtcars, gear)
```

### 

`slice()` lets you index rows by their integer locations. It allows you to select, remove, and duplicate rows.

### Exercise 2

Copy the previous code and add it as a parameter in `slice()`.

```{r design-for-the-pipe--2, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--2-hint-1, eval = FALSE}
slice(...(mtcars, gear))
```

```{r include = FALSE}
slice(arrange(mtcars, gear))
```

### 

As you can see, an empty tibble was printed out. This is because the number of rows to be extracted was never specified.

### Exercise 3

Copy the previous code. Add the parameter `5` in `slice()`.

```{r design-for-the-pipe--3, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--3-hint-1, eval = FALSE}
slice(...(mtcars, gear), 5)
```

```{r include = FALSE}
slice(arrange(mtcars, gear), 5)
```

### 

Notice how that the output is the 5th row in `mtcars`, which is sorted by number of gears. To extract multiple consecutive rows, we can use `:`

### Exercise 4

Copy the previous code and replace the parameter `5` with `1:10`.

```{r design-for-the-pipe--4, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--4-hint-1, eval = FALSE}
slice(arrange(mtcars, gear), ...)
```

```{r include = FALSE}
slice(arrange(mtcars, gear), 1:10)
```

### 

This way of slicing a data set can be hard to read and might confuse the audience looking at your code. Using the `|>` operator can help with user readability.

### Exercise 5

We will continue to use the `mtcars` data set, as we are quite comfortable with it up to this point. Pipe `arrange(gear)` after typing `mtcars` on the first line with the use of the `|>` operator.

```{r design-for-the-pipe--5, exercise = TRUE}

```

```{r design-for-the-pipe--5-hint-1, eval = FALSE}
mtcars |>
  arrange(...)
```

```{r include = FALSE}
mtcars |>
  arrange(gear)
```

### Exercise 6

Copy the previous. Extract the first 10 rows using `:` of the ordered data set by adding `slice()` to the pipe.

```{r design-for-the-pipe--6, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--6-hint-1, eval = FALSE}
mtcars |>
  arrange(...) |>
  slice(...)
```

```{r include = FALSE}
mtcars |>
  arrange(gear) |>
  slice(1:10)
```

### 

User readability is crucial to making coding a more friendly environment for collaboration when working on projects involving multiple entities.

### Exercise 7

When plotting using **ggplot**, the pipe operator becomes invalid. To `"pipe"` in when plotting, use the `+` symbol. Run the code below to observe plotting.

```{r design-for-the-pipe--7, exercise = TRUE}
ggplot(mtcars, aes(x = wt, y = mpg)) +
  geom_point() + 
  geom_smooth(method = lm)
```

### 

In many real-world cases, the element-wise operation of interest is too complex for a vectorized solution. In such a case, a good approach is to write a function to do the computations.

### 

The *structure* of a function is as follows: 

function_name <- function(arg1, arg2, ...){                             return("something")                                             }

*Example function*:

add_numbers <- function(num1, num2){                                  sum <- num1 + num2                                                  return(sum)                                                       }

result <- add_numbers(5, 3)                             print(result)

```{r}
result <- add_numbers(5, 3)
print(result)
```

### Exercise 8

We will be computing the log ratio of  the mpg vs weight from the cars in them `mtcars` data set. Make the function for the `compute_log_ratio` and set it equal to a function with arguments `mpg` and `wt`. Remember to follow this expression with `{}`.

```{r design-for-the-pipe--8, exercise = TRUE}

```

```{r design-for-the-pipe--8-hint-1, eval = FALSE}
compute_log_ratio <- ...(mpg, wt){
  
}
```

```{r include = FALSE}
compute_log_ratio <- function(mpg, wt){
  
}
```

### 

We can also have parameters of functions that are set to certain values within in function(). An example would be fctn_name <- function(..., log_base = exp(1)). You should not use this as a argument, however, you *call* the function.

### Exercise 9

Since we are computing the log ratio, we need to set the base of the log to 1. Copy the previous code and add the parameter `log_base = exp(1)`.

```{r design-for-the-pipe--9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--9-hint-1, eval = FALSE}
...<- function(..., ..., log_base = exp(...)){
  
}
```

```{r include = FALSE}
compute_log_ratio <- function(mpg, wt, log_base = exp(1)){
  
}
```

### 

There are certain functions were you do not have to necessarily have a return() statement. Rather you can have the function print a desired value based on the arguments. However, it is best practice to have the function return some value.

### Exercise 10

It is crucial to have the return statement in the function. Copy the previous code and add the `return()` statement within the `{}` brackets.

```{r design-for-the-pipe--10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--10-hint-1, eval = FALSE}
...{
  ...()
}
```

```{r include = FALSE}
compute_log_ratio <- function(mpg, wt, log_base = exp(1)){
  return()
}
```

### 

The return() statement exits the function and returns the value you desire. It can be any R object, such as a number, character, vector, list, or even NULL.

### Exercise 11

The log() function, in this case, will take the ratio between `mpg/wt` and take a log base, which was set to exp(1). First, copy the previous code and within the return statement, return log() with the first argument being `mpg/wt`.

```{r design-for-the-pipe--11, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--11-hint-1, eval = FALSE}
...{
  return(...(mpg/wt))
}
```

```{r include = FALSE}
compute_log_ratio <- function(mpg, wt, log_base = exp(1)){
  return(log(mpg/wt))
}
```

### Exercise 12

Copy the previous code and add `base` as a parameter for `log()`, which is equal to the log_base argument set in the function parameters for `compute_log_ratio`.

```{r design-for-the-pipe--12, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--12-hint-1, eval = FALSE}
...{
  return(log(mpg/wt, base = ...))
}
```

```{r include = FALSE}
compute_log_ratio <- function(mpg, wt, log_base = exp(1)){
  return(log(mpg/wt), base = log_base)
}
```

### 

To access any function that we have created, we must call this function in order to use it and give it the right number of parameters.

### Exercise 13

We must call the function outside of the function. Set `result` to `compute_log_ratio()`. This might throw an error, but that will be fixed later.

```{r design-for-the-pipe--13, exercise = TRUE}

```

```{r design-for-the-pipe--13-hint-1, eval = FALSE}
result <- ...()
```

```{r include = FALSE}
#result <- compute_log_ratio()
```

### Exercise 14

Set the arguments of the function to the columns `mpg` and `wt` from `mtcars` using the `$` symbol.

```{r design-for-the-pipe--14, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--14-hint-1, eval = FALSE}
result <- compute_log_ratio(mtcars$..., mtcars$...)
```

```{r include = FALSE}
#result <- compute_log_ratio(mtcars$mpg, mtcars$wt)
```

### Exercise 15

Finally, copy the previous code and print this value on the next line using `print()`. You should get a series of values with the compute log ratios between `mpg` and `wt`.

```{r design-for-the-pipe--15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--15-hint-1, eval = FALSE}
print(...)
```

```{r include = FALSE}
print(result)
```

### 

When we design for functional programming, it is important that the output depends only on the inputs and that the function has no side effects. 

### Exercise 16

We will be using the **Tidyverse** package **purr** to further examine the uses of functional programming. The most basic function, map(), always returns a list and uses the basic syntax of `map(vector, function)`.

First, within the function head(), add the parameter `mtcars$mpg` and `3`, since we want to look at the first 3 rows of the `mpg` column.

```{r design-for-the-pipe--16, exercise = TRUE}

```

```{r design-for-the-pipe--16-hint-1, eval = FALSE}
head(mtcars$mpg, ...)
```

```{r include = FALSE}
head(mtcars$mpg, 3)
```

### 

There are many types of map function in the **purr** package, such as `map_dbl()`, `map2_dbl()`, etc.

### Exercise 17

Copy the previous code. Pipe the code to `map()` and add the parameter `sqrt`, as we want to take the square root of the `mpg` column.

```{r design-for-the-pipe--17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--17-hint-1, eval = FALSE}
...|>
  map(sqrt)
```

```{r include = FALSE}
head(mtcars$mpg, 3) |>
  map(sqrt)
```

### 

As you can see, `map()` returned the list of the `mpg`  of the first 3 rows of `mtcars` square rooted.

### Exercise 18

`map_dbl()` returns the a vector compared to a list returned when `map()` is called. Copy the previous code and change map() to `map_dbl()`.

```{r design-for-the-pipe--18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r design-for-the-pipe--18-hint-1, eval = FALSE}
head(mtcars$mpg, 3) |>
  map_dbl(...)
```

```{r include = FALSE}
head(mtcars$mpg, 3) |>
  map_dbl(sqrt)
```

### 

Great Job! You now have a better understanding of how the pipe operator `|>` works and how functional programming can help create a more understandable solution to complex problems.

## Tidyverse Syntax
### 

Let's begin our discussion of tidyverse syntax by exploring more deeply what a tibble is, and how tibbles work. Tibbles have slightly different rules than basic data frames in R.

### Exercise 1

Here are some of the aspects of `data.frame()`:

-   The column names should be non-empty

-   The row names should be unique

-   The data stored in a data frame can be of numeric, factor or character type

-   Each column should contain same number of data items

Type in `data.frame()`.

```{r tidyverse-syntax-1, exercise = TRUE}

```

```{r include = FALSE}
data.frame()
```

### 

To initialize columns in a data frame, you must give a name within "" and set it equal to a certain desired values.

### Exercise 2

Copy the previous code. Add the column name parameter, `"column 1"`, in the `data.frame()` function.

```{r tidyverse-syntax-2, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-2-hint-1, eval = FALSE}
data.frame("...")
```

```{r include = FALSE}
data.frame("column 1")
```

### 

As you can see, there is only one row with the name of the column. The column name, however, seems hard to read and is confusing.

### Exercise 3

`check.names = FALSE` will eliminate any confusion of the true column name. Copy the previous code and add that as the parameter of `data.frame()`.

```{r tidyverse-syntax-3, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-3-hint-1, eval = FALSE}
data.frame("...", check.names = ...)
```

```{r include = FALSE}
data.frame("column 1", check.names = FALSE)
```

### Exercise 4

Now lets assign values to the column using the `=` sign. Copy the previous code and set the column name to values from 1 to 3.

```{r tidyverse-syntax-4, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-4-hint-1, eval = FALSE}
"Remember to use the : symbol to get multiple consecutive numbers."
```

```{r tidyverse-syntax-4-hint-2, eval = FALSE}
data.frame("..." = 1:3, check.names = ...)
```

```{r include = FALSE}
data.frame("column 1" = 1:3, check.names = FALSE)
```

### Exercise 5

Now to create another row, copy the previous code and add the column name parameter `two` to `data.frame()` and set it equal to the values 4 to 6. Set this data frame to `df`.

```{r tidyverse-syntax-5, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-5-hint-1, eval = FALSE}
df <- data.frame("column 1" = 1:3, `...` = 4:6, check.names = ...)
```

```{r include = FALSE}
df <- data.frame("column 1" = 1:3, `two` = 4:6, check.names = FALSE)
```

### 

Tibbles are the modern version of data frames. They only print the first ten rows and print column names that fit.

### Exercise 6

Copy the previous code. Replace `data.frame()` with `tibble()`, keeping the first two parameters the same and deleting the `check.names` parameter. Set this tibble to `tbl` using the assignment operator `<-`.

```{r tidyverse-syntax-6, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-6-hint-1, eval = FALSE}
tbl <- tibble(`...` = 1:3, `...` = 4:6)
```

```{r include = FALSE}
tbl <- tibble(`column 1` = 1:3, `two` = 4:6)
```

### 

Tibbles also prevent one of the most common R errors: dropping dimensions. If a standard data frame subsets the columns down to a single column, the object is converted to a vector. Tibbles never do this.

### Exercise 7

Within the brackets of `tbl[]` and `df[]` (on two different lines), type in `, "two"` and compare the differences of the printed outcome.

```{r tidyverse-syntax-7, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-7-hint-1, eval = FALSE}
tbl[, ...]
df[, ...]
```

```{r include = FALSE}
tbl[, "two"]
df[, "two"]
```

### 

The tibble keeps the structure of a column while the data frame turns it into a vector of values.

### Exercise 8

Standard data frames enable partial matching of arguments so that code using only a portion of the column names still works. Extract the `two` column from the data frame `df` using the `tw`, which is only the partial name of the column `two`.

```{r tidyverse-syntax-8, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-8-hint-1, eval = FALSE}
...$tw
```

```{r include = FALSE}
df$tw
```

### 

As you can see, even though the partial name of the column was called, the data frame recognized it as the column `two` and printed the desired column.

### Exercise 9

Copy the previous code. Replace `df` with `tbl` and press "Run Code".

```{r tidyverse-syntax-9, exercise = TRUE}

```

<button onclick="transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-9-hint-1, eval = FALSE}
...$tw
```

```{r include = FALSE}
tbl$tw
```

### 

The warning message: "Unknown or uninitialized column: `tw`" shows up because the full column name must be entered to extract the correct column from the tibble. Tibbles prevent partial matching from happening since it can lead to accidental errors.

### Exercise 10

To demonstrate some syntax, let's use tidyverse functions to read in data that could be used in modeling. The data set comes from the city of Chicago's data portal and contains daily ridership data for the city's elevated train stations. The data set has columns for:

-   the station identifier (numeric)

-   the station name (character)

-   the date (character in mm/dd/yyyy format)

-   the day of the week (character)

-   the number of riders (numeric)

First, we will be using the **lubridate** package to convert the dates into the proper R format. Load the **lubridate** library using `library()`.

```{r tidyverse-syntax-10, exercise = TRUE}

```

```{r tidyverse-syntax-10-hint-1, eval = FALSE}
library(...)
```

```{r include = FALSE}
library(lubridate)
```

### Exercise 11

We will also need the **readr** package to use functions that deal with csv files. Load the library using `library()`.

```{r tidyverse-syntax-11, exercise = TRUE}

```

```{r tidyverse-syntax-11-hint-1, eval = FALSE}
library(...)
```

```{r include = FALSE}
library(readr)
```

### Exercise 12

Next, we will need to use the data set we are looking at. Run the code to store the data set in the variable `url`.

```{r tidyverse-syntax-12, exercise = TRUE}
url <- "https://data.cityofchicago.org/api/views/5neh-572f/rows.csv?accessType=DOWNLOAD&bom=true&format=true"
```

### 

This pipeline of operations illustrates why the tidyverse is popular. A series of data manipulations is used that have simple and easy to understand functions for each transformation; the series is bundled in a streamlined, readable way. 

### Exercise 13

Now that the data set is assigned to `url`, we will now read the data using the function `read_csv()`. Within in `read_csv()`, put `url` as the parameter and set the expression equal to "chicago". Hit "Run Code".

```{r tidyverse-syntax-13, exercise = TRUE}

```

```{r tidyverse-syntax-13-hint-1, eval = FALSE}
chicago <- read_csv(...)
```

```{r include = FALSE}
chicago <- read_csv(url)
```

### 

In R, the head() function views first few rows of a data frame or a vector without displaying the entire data set.

### Exercise 14

Select the columns `stationname, date, rides` by piping select() to `chicago`. 

```{r tidyverse-syntax-14, exercise = TRUE}

```

```{r tidyverse-syntax-14-hint-1, eval = FALSE}
chicago |>
  select(..., ..., ...)
```

```{r include = FALSE}
chicago |>
  select(stationname, date, rides)
```

### 

Pipelines are incredibly useful in modeling workflows but modeling pipelines can return, instead of a data frame, objects such as model components.

### Exercise 15

We want to reduce confusion with one of the column names and make it more clear to the what the data is portraying. Copy the previous code and rename `stationname` to station using the `=` operator within `select()`.

```{r tidyverse-syntax-15, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-15-hint-1, eval = FALSE}
chicago |>
  select(... = stationname, date, rides)
```

```{r include = FALSE}
chicago |>
  select(station = stationname, date, rides)
```

### 

There are specialized variants of map() that return values when we know or expect that the function will generate one of the basic vector types.

### Exercise 16

We need to change the dates in the data set to the correct R form using `mdy()`. Copy the previous code and pipe it to mutate(). Inside the function, add `date` as the parameter for `mdy()` and set that expression to `date`.

```{r tidyverse-syntax-16, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-16-hint-1, eval = FALSE}
... |>
  mutate(date = mdy(...))
```

```{r include = FALSE}
chicago |>
  select(station = stationname, date, rides) |>
  mutate(date = mdy(date))
```

### 

For this reason, it is critical that R code be easy to work with to accomplish your goals. Documentation, training, accessibility, and other factors play an important part in achieving this. 

### Exercise 17

We also want to make the rides in the units of 1k. Copy the previous code and set `rides` equal to `rides/1000`.

```{r tidyverse-syntax-17, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-17-hint-1, eval = FALSE}
... |>
  mutate(date = mdy(...), rides = .../1000)
```

```{r include = FALSE}
chicago |>
  select(station = stationname, date, rides) |>
  mutate(date = mdy(date), rides = rides/1000)
```

### 

The tidyverse focuses on designing R packages and functions that can be easily understood and used by a broad range of people. Both historically and today, a substantial percentage of R users are not people who create software or tools but instead people who create analyses or models. 
 
### Exercise 18

To summarize the records using the maximum number of rides, we first need to group the data by `date` and `station`. Copy the previous code and pipe `group_by()` with the parameters being `date` and `station`.

```{r tidyverse-syntax-18, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-18-hint-1, eval = FALSE}
... |>
  group_by(..., ...)
```

```{r include = FALSE}
chicago |>
  select(station = stationname, date, rides) |>
  mutate(date = mdy(date), rides = rides/1000) |>
  group_by(date, station)
```

### 

From Wickham et al. (2019):

“At a high level, the tidyverse is a language for solving data science challenges with R code. Its primary goal is to facilitate a conversation between a human and a computer about data. Less abstractly, the tidyverse is a collection of R packages that share a high-level design philosophy and low-level grammar and data structures, so that learning one package makes it easier to learn the next.”

### Exercise 19

Now that we have grouped the data set by date and station, we will now summarize it by the maximum rides using the `summarize()` functin. Copy the previous code and pipe it to `summarize()`. Add the parameter of the max `rides` using them `max()` function and setting the expression equal to `rides`.

```{r tidyverse-syntax-19, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-19-hint-1, eval = FALSE}
... |>
  summarize(rides = max(...))
```

```{r include = FALSE}
chicago |>
  select(station = stationname, date, rides) |>
  mutate(date = mdy(date), rides = rides/1000) |>
  group_by(date, station) |>
  summarize(rides = max(rides))
```

### 

This approach enables more people to learn R and achieve their analysis goals, and adopting these same principles for modeling in R has the same benefits.

### Exercise 20

Finally, we do not want the grouped structure to remain after summarizing the data by the maximum rides. Copy the previous code and add `.groups = "drop"` to `summarize()`.

```{r tidyverse-syntax-20, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r tidyverse-syntax-20-hint-1, eval = FALSE}
... |>
  summarize(rides = max(rides), .groups = "...")
```

```{r include = FALSE}
chicago |>
  select(station = stationname, date, rides) |>
  mutate(date = mdy(date), rides = rides/1000) |>
  group_by(date, station) |>
  summarize(rides = max(rides), .groups = "drop")
```

### 

As such, R users do not typically have (or need) computer science backgrounds, and many are not interested in writing their own R packages.

### 

Great work! You now should have a greater understanding of the tidyverse syntax such as data frames, tibbles, and functions such as mutate(), summarize(), etc.

## Summary
### 

This tutorial covered [Chapter 2: Tidyverse Principles](https://www.tmwr.org/tidyverse.html#tidyverse-principles) from [*Tidy Modeling with R*](https://www.tmwr.org/) by Max Kuhn and Julia Silge. We briefly discused the important principles of the [**tidyverse**](https://www.tidyverse.org/packages/) design philosophy and how they apply in the context of modeling software that is easy to use and supports good statistical practices. You have learned the relationship between **tidymodels** and **tidyverse**, as [**tidymodels**](https://www.tidymodels.org/packages/) applies **tidyverse** principles to building models.

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
