---
title: The Ames Housing Data
author: Pratham Kancherla and David Kane
tutorial:
  id: the-ames-housing-data
output:
  learnr::tutorial:
    progressive: yes
    allow_skip: yes
runtime: shiny_prerendered
description: 'Tutorial for Chapter 4: The Ames Housing Data'
---

```{r setup, include = FALSE}
library(learnr)
library(tidymodels)
library(tidyverse)
library(tutorial.helpers)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 

gg_hist <- ggplot(ames, aes(x = Sale_Price)) + 
  geom_histogram(bins = 50, col= "white") +
  scale_x_log10()
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

## Introduction
### 

This tutorial covers [Chapter 4: The Ames Housing Data](https://www.tmwr.org/ames.html) from [*Tidy Modeling with R*](https://www.tmwr.org/) by Max Kuhn and Julia Silge. We will introduce the Ames housing data set [(De Cock 2011)](https://www.tmwr.org/ames.html#ref-ames), which we will use in modeling examples in later tutorials. Exploratory data analysis, like what we walk through in this tutorial, is an important first step in building a reliable model.

## Exploring Features of Homes in Ames
### 

The data set contains information on 2,930 properties in Ames, Iowa, including columns related to:

-   house characteristics (bedrooms, garage, fireplace, pool, porch, etc.)

-   location (neighborhood)

-   lot information (zoning, shape, size, etc.)

-   ratings of condition and quality

-   sale price

### Exercise 1

The Ames data has been made available through the **modeldata** package, which is a built in **tidymodels** package.

Load the library **tidymodels** using `library()`.

```{r exploring-features-of-homes-in-1, exercise = TRUE}

```

```{r exploring-features-of-homes-in-1-hint-1, eval = FALSE}
library(...)
```

```{r exploring-features-of-homes-in-1-test, include = FALSE}
library(tidymodels)
```

### 

The core **tidymodels** packages: [**rsample**](https://rsample.tidymodels.org/), [**parsnip**](https://parsnip.tidymodels.org/), [**recipes**](https://recipes.tidymodels.org/), [**workflows**](https://workflows.tidymodels.org/), [**tune**](https://tune.tidymodels.org/), [**yardstick**](https://yardstick.tidymodels.org/), [**broom**](https://broom.tidymodels.org/), [**dials**](https://dials.tidymodels.org/)

### Exercise 2

Now load the data `ames` from the package using the `data()` function.

```{r exploring-features-of-homes-in-2, exercise = TRUE}

```

```{r exploring-features-of-homes-in-2-hint-1, eval = FALSE}
data(...)
```

```{r exploring-features-of-homes-in-2-test, include = FALSE}
data(ames)
```

### 

In R, the dim() function is used to retrieve or set the dimensions of an object, such as a matrix, array, or data frame. The dim() function returns a vector with two elements representing the number of rows and columns (dimensions) of the object.

### Exercise 3

We want to look at how many rows and columns are in `ames`. Use `dim()` with `ames` as the parameter to retrieve a vector of (# of rows, # of columns).

```{r exploring-features-of-homes-in-3, exercise = TRUE}

```

```{r exploring-features-of-homes-in-3-hint-1, eval = FALSE}
dim(...)
```

```{r exploring-features-of-homes-in-3-test, include = FALSE}
dim(ames)
```

### 

Changes made to the data in the `modeldata` package are such that in the raw data, if a house did not have a particular feature, it was implicitly encoded as missing, the categorical predictors were converted to R’s factor data type, and quality descriptors for each house were removed since they are more like outcomes than predictors.

### Exercise 4

Let’s start our exploratory data analysis by focusing on the outcome we want to predict: the last sale price of the house (in USD). We can create a histogram to see the distribution of sale prices.

Type in ames to see the data that we are looking at.

```{r exploring-features-of-homes-in-4, exercise = TRUE}

```

```{r exploring-features-of-homes-in-4-hint-1, eval = FALSE}
ames
```

### 

The root mean squared error (RMSE) is a common performance metric used in regression models. It uses the difference between the observed and predicted values in its calculations.

### Exercise 5

Copy the previous code and pipe it to ggplot() to start creating a histogram.

```{r exploring-features-of-homes-in-5, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r exploring-features-of-homes-in-5-hint-1, eval = FALSE}
ames |>
  ...()
```

```{r exploring-features-of-homes-in-5-test, include = FALSE}
ames |>
  ggplot()
```

### 

In R, ggplot() is a function from the **ggplot2** package, which is a powerful and widely-used package for creating visualizations. 

### Exercise 6

We need to establish the x-axis on the graph. Copy the previous code and, using `aes()` within in `ggplot()`, set `x` equal to `Sale_Price`.

```{r exploring-features-of-homes-in-6, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r exploring-features-of-homes-in-6-hint-1, eval = FALSE}
... |>
  ggplot(aes(x = ...))
```

```{r exploring-features-of-homes-in-6-test, include = FALSE}
ames |>
  ggplot(aes(x = Sale_Price))
```

### 

The disadvantages of transforming the outcome mostly relate to interpretation of model results.

### Exercise 7

Now we will created the histogram. Copy the previous code and add the geom_hist() function to ggplot() using the `+` symbol.

```{r exploring-features-of-homes-in-7, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r exploring-features-of-homes-in-7-hint-1, eval = FALSE}
... +
  geom_histogram()
```

```{r exploring-features-of-homes-in-7-test, include = FALSE}
ames |>
  ggplot(aes(x = Sale_Price)) +
    geom_histogram()
```

### 

In **ggplot2**, geom_histogram() is a function used to create a histogram, which is a graphical representation of the distribution of a continuous variable. A histogram divides the data into intervals (bins) and displays the frequency or count of data points falling into each bin.

### Exercise 8

Lets add `bins` to the histogram. Copy the previous code and in geom_histogram(), add the parameter `bins`, setting it equal to `50`.

```{r exploring-features-of-homes-in-8, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r exploring-features-of-homes-in-8-hint-1, eval = FALSE}
... +
  geom_histogram(bins = ...)
```

```{r exploring-features-of-homes-in-8-test, include = FALSE}
ames |>
  ggplot(aes(x = Sale_Price)) +
    geom_histogram(bins = 50)
```

### 

This plot shows us that the data are right-skewed; there are more inexpensive houses than expensive ones. When modeling this outcome, a strong argument can be made that the price should be log-transformed.

### Exercise 9

Lets add `col` (color) to the histogram. Copy the previous code and in geom_histogram(), add the parameter `col`, setting it equal to `"white"`.

```{r exploring-features-of-homes-in-9, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r exploring-features-of-homes-in-9-hint-1, eval = FALSE}
... +
  geom_histogram(bins = 50, col = "...")
```

```{r exploring-features-of-homes-in-9-test, include = FALSE}
ames |>
  ggplot(aes(x = Sale_Price)) +
    geom_histogram(bins = 50, col = "white")
```

### 

From a statistical perspective, a logarithmic transform may also stabilize the variance in a way that makes inference more legitimate. 

### Exercise 10

Copy the previous code and add `scale_x_log10()`.

```{r exploring-features-of-homes-in-10, exercise = TRUE}

```

<button onclick = "transfer_code(this)">Copy previous code</button>

```{r exploring-features-of-homes-in-10-hint-1, eval = FALSE}
... +
  scale_x_...()
```

```{r exploring-features-of-homes-in-10-test, include = FALSE}
ames |>
  ggplot(aes(x = Sale_Price)) +
    geom_histogram(bins = 50, col = "white") +
    scale_x_log10()
```

### 

The advantages of this type of transformation are that no houses would be predicted with negative sale prices and that errors in predicting expensive houses will not have an undue influence on the model. 

### 

Great Job! You now understood the basic concept of exploratory data analysis by analyzing the sale price of homes in Ames, Iowa. 

<!-- DK: leave comments about decision to not do all graphics. -->

## Summary
### 

This tutorial covered [Chapter 4: The Ames Housing Data](https://www.tmwr.org/ames.html) from [*Tidy Modeling with R*](https://www.tmwr.org/) by Max Kuhn and Julia Silge. We introduced the Ames housing data set [(De Cock 2011)](https://www.tmwr.org/ames.html#ref-ames), which we will use in modeling examples in later tutorials. Exploratory data analysis, like what we walk through in this tutorial, is an important first step in building a reliable model and you now a basic understanding of this concept.

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
