---
title: A Review of R Modeling Fundamentals
author: David Kane and Aryan Kancherla
tutorial:
  id: a-review-of-r-modeling-fundamentals
output: 
  learnr::tutorial:
    progressive: true
    allow_skip: true
runtime: shiny_prerendered
description: "Tutorial for Chapter 3: A Review of R Modeling Fundamentals"
---

```{r setup, include = FALSE}
library(learnr)
library(tutorial.helpers)
library(tidyverse)
knitr::opts_chunk$set(echo = FALSE)
options(tutorial.exercise.timelimit = 60, 
        tutorial.storage = "local") 
```

```{r copy-code-chunk, child = system.file("child_documents/copy_button.Rmd", package = "tutorial.helpers")}
```

```{r info-section, child = system.file("child_documents/info_section.Rmd", package = "tutorial.helpers")}
```

<!-- CHECKLIST BEFORE STARTING: -->
<!-- * Edit yaml at the top of this file -->
<!-- * Save the file as "tutorial.Rmd" in a new directory under inst/tutorials/. -->
<!-- * Load any necessary libraries for the tutorial in the first code chunk -->
<!-- * Review: https://ppbds.github.io/tutorial.helpers/articles/instructions.html -->
<!-- * Delete this and the other commented instructions below. -->

## Introduction
###


This tutorial covers [Chapter 3: A Review of R Modeling Fundamentals](https://www.tmwr.org/base-r.html) from [*Tidy Modeling with R*](https://www.tmwr.org/) by Max Kuhn and Julia Silge. This chapter is a brief illustration of core language conventions that are important to be aware of even if you never use base R for models at all. This chapter is not exhaustive, but it provides readers (especially those new to R) the basic, most commonly used motifs.



## Modeling in base R
###

To demonstrate some fundamentals for modeling in base R, let’s use experimental data from McDonald (2009), by way of Mangiafico (2015), on the relationship between the ambient temperature and the rate of cricket chirps per minute. Data were collected for two species: O. exclamationis and O. niveus. The data are contained in a data frame called crickets with a total of 31 data points.

### Exercise 1

Load the **tidyverse** library using `library()`.

```{r modeling-in-base-r-1, exercise = TRUE}

```

```{r modeling-in-base-r-1-hint, eval = FALSE}
library(...)
```

```{r, include=FALSE}
library(tidyverse)
```

###


## Summary
###

<!-- Two to four sentences which bring the lessons of the tutorial together for the student. What do they know now that they did not know before? How does this tutorial connect to other tutorials? OK if this is very similar to the Introduction. You made a promise as to what they would learn. You (we hope!) kept that promise.-->

```{r download-answers, child = system.file("child_documents/download_answers.Rmd", package = "tutorial.helpers")}
```
